---
title: "In-Place Operations in R"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{In-Place Operations in R}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(inplaceops)  # Replace with your actual package name
```

# Introduction

This vignette demonstrates the use of in-place operations provided by the inplaceOps package. These operations allow you to modify variables directly, making your code more concise and potentially more efficient.

## Arithmetic Operations

### Addition

```{r}
x <- 5
x %+=% 3
print(x)
```

### Subtraction

```{r}
y <- 10
y %-=% 4
print(y)
```

## Vector Operations

### Concatenation

```{r}
v <- c(1, 2, 3)
v %c=% c(4, 5)
print(v)
```

### Union

```{r}
set1 <- c(1, 2, 3)
set1 %union=% c(3, 4, 5)
print(set1)
```

### Set Difference

```{r}
set2 <- c(1, 2, 3, 4, 5)
set2 %setdiff=% c(2, 4)
print(set2)
```

## Operations by Variable Name

These functions allow you to modify variables by their name as a string.

### Addition

```{r}
z <- 7
assignPlus("z", 5)
print(z)
```

### Concatenation

```{r}
words <- c("hello", "world")
assignC("words", "!")
print(words)
```

### Set Difference

```{r}
numbers <- c(1, 2, 3, 4, 5)
assignSetdiff("numbers", c(2, 4))
print(numbers)
```

# Conclusion

These in-place operations can make your R code more readable and potentially more efficient, especially when working with large datasets or in loops where you're repeatedly modifying the same variable.
